---
title: "Chapter Three Homework: Due Wednesday the 27th"
author: "Your Name Here"
date: '`r format(Sys.time(), "%b %d, %Y")`'
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, fig.align = "center", warning = FALSE, message = FALSE)
library(tidyverse)
library(resampledata)
```

Exercise 3.5:

In the Flight Delays Case Study in Section 1.1,

    a. The data contain flight delays for two airlines, American Airlines and United Airlines.  Conduct a two-sided permutation test to see if the mean delay times between the two carriers are statistically significant.
    
    b. The flight delays occured in May and June of 2009.  Conduct a two-sided permutation test to see if the difference in mean delay times between the 2 months is statistically significant.
    


```{r}
data("FlightDelays")
glimpse(FlightDelays)

# a. Your code here

``` 

> SOLUTION: 

```{r}
# b. Your code here
```

> SOLUTION: 


Exercise 3.8: 

In the Flight Delays Case Study in Section 1.1,
    
    a. Find the 25% trimmed mean of the delay times for United Airlines and American Airlines.
    
    b. Conduct a two-sided test to see if the difference in trimmed means is statistically significant.
    
```{r}
# a. Your code here
```

> SOLUTION: 

```{r}
# b. Your code here
```

> SOLUTION:    
    
Exercise 3.9: 


In the Flight Delays Case Study in Section 1.1,

    a. Compute the proportion of times the flights in May and in June were delayed more than 20 min, and conduct a two-sided test of whether the difference between months is statistically significant.
    
    b. Compute the variance of the flight delay times in May and June and then conduct a two-sided test of whether the ratio of variances is statistically significantly different from 1.
    
```{r}
# a. Your code here
```

> SOLUTION:

```{r}
# b. Your code here
```

> SOLUTION:



