---
title: "Chapter Two Homework: Due Wednesday the 6th"
author: "Your Name Here"
date: '`r format(Sys.time(), "%b %d, %Y")`'
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, fig.align = "center", warning = FALSE, message = FALSE)
library(tidyverse)
library(resampledata)
```

1) Exercise 2.7 MODIFIED:

Import data from the black spruce case study in Section 1.10 in to `R`.

> SOLUTION: 

```{r}
# Your code goes here

```

a) Compute the numeric summaries for the height changes (`Ht.change`) of the seedlings.

> SOLUTION: 

```{r}
# Your code goes here

```


b) Create a histogram and normal quantile plot for the height changes of the seedlings. Is the distribution approximately normal?

> SOLUTION: 

```{r}
# Your code goes here

```


c) Create a boxplot to compare the distribution of the change in diameters of the seedlings (`Di.change`) grouped by whether or not they were in fertilized plots.

> SOLUTION: 

```{r}
# Your code goes here

```

d) Use Ch 5 of MD: Data Wrangling via `dplyr` to find the numeric summaries of the diameter changes for the two levels fertilization.

> SOLUTION: 

```{r}
# Your code goes here

```

e) Use `ggplot` to create a scatter  plot of the height changes against the diameter changes, describe the relationship.

> SOLUTION: 

```{r}
# Your code goes here

```








