---
title: "Homework 1 (Chapter Two): Due Thursday the 6th"
author: "Your Name Here"
date: '`r format(Sys.time(), "%b %d, %Y")`'
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, fig.align = "center", warning = FALSE, message = FALSE)
library(tidyverse)
library(resampledata)
```

> Note: You need to create a RMarkdown document to do your HW. Make sure to show 
  1. Your code,
  2. The output, 
  3. The descriptions where necessary.


1) Exercise 2.7 MODIFIED:

Import data from the black spruce case study in Section 1.10 in to `R`.

> SOLUTION: 

```{r}
# Your code goes here

```

a) Compute the numeric summaries (Mean, Standard deviation, Minimum, Median, IQR, Range, Maximum, etc.) for the height changes (`Ht.change`) of the seedlings.

> SOLUTION: 

```{r}
# Your code goes here

```


b) Create a histogram and normal quantile plot for the height changes of the seedlings. Is the distribution approximately normal?

> SOLUTION: 

```{r}
# Your code goes here

```


c) Create a boxplot to compare the distribution of the change in diameters of the seedlings (`Di.change`) grouped by whether or not they were in fertilized plots. Describe the graph.

> SOLUTION: 

```{r}
# Your code goes here

```

d) Use `%>%` operator via `dplyr` to find the Mean, Standard deviation, Median, IQR in the same order of the diameter changes for the two levels fertilization.

> SOLUTION: 

```{r}
# Your code goes here

```

e) Use `ggplot` to create a scatter  plot of the height changes against the diameter changes, describe the relationship.

> SOLUTION: 

```{r}
# Your code goes here

```








