---
title: "Homework 2: Ch3 MSWR: Due Tuesday the 25th"
author: "Your Name Here"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, fig.align = "center", warning = FALSE, message = FALSE)
library(tidyverse)
library(resampledata)
```




```{r include=FALSE}
#Exercise 3.5:

#In the Flight Delays Case Study in Section 1.1,

#    a. The data contain flight delays for two airlines, American Airlines and United Airlines.  Conduct a #two-sided permutation test to see if the mean delay times between the two carriers are statistically significant.
    
#   b. The flight delays occured in May and June of 2009.  Conduct a two-sided permutation test to see if the #difference in mean delay times between the 2 months is statistically significant.
    

data("FlightDelays")
glimpse(FlightDelays)

# a. Your code here

library(moderndive)
library(resampledata)
library(nycflights13)
set.seed(222)

#FD <- read.csv("http://www1.appstate.edu/~arnholta/Data/FlightDelays.csv")
data("FlightDelays")

str(FlightDelays)
# a.
sims <- 10^4 - 1

an <- FlightDelays %>%
  group_by(Carrier) %>%
  summarize(Mean = mean(Delay), N = n())
an

obs <- an[2,2] - an[1,2]
obs_diff <- obs$Mean
#
md <- numeric(sims)
for(i in 1:sims){
  index <- sample(4029, size = 1123, replace = FALSE)
  md[i] <- mean(FlightDelays$Delay[index]) - mean(FlightDelays$Delay[-index])
}

pvalue <- 2*((sum(md >= obs_diff) + 1)/(sims + 1))
pvalue


#FD <- read.csv("http://www1.appstate.edu/~arnholta/Data/FlightDelays.csv")
data("FlightDelays")

str(FlightDelays)
# a.
sims <- 10^4 - 1

an <- FlightDelays %>%
  group_by(Month) %>%
  summarize(Mean = mean(Delay), N = n())
an

obs <- an[2,2] - an[1,2]
obs_diff <- obs$Mean
#
md <- numeric(sims)
for(i in 1:sims){
  index <- sample(4029, size = 2030, replace = FALSE)
  md[i] <- mean(FlightDelays$Delay[index]) - mean(FlightDelays$Delay[-index])
}

pvalue <- 2*((sum(md >= obs_diff) + 1)/(sims + 1))
pvalue
```



Exercise 3.8: 

In the Flight Delays Case Study in Section 1.1,
    
  a. Find the 25% trimmed mean of the delay times for United Airlines and American Airlines.
    
  b. Conduct a two-sided test to see if the difference in trimmed means is statistically significant.
    
```{r}
# a. Your code here
```

> SOLUTION: 

```{r}
# b. Your code here
```

> SOLUTION:    
    
Exercise 3.9: 


In the Flight Delays Case Study in Section 1.1,

  a. Compute the proportion of times the flights in May and in June were delayed more than 20 min, and conduct a two-sided test of whether the difference between months is statistically significant.
    
  b. Compute the variance of the flight delay times in May and June and then conduct a two-sided test of whether the ratio of variances is statistically significantly different from 1.
    
```{r}
# a. Your code here
```

> SOLUTION:

```{r}
# b. Your code here
```

> SOLUTION:



