---
title: "Chapter 7 of MD Homework: Due Thursday April 4"
author: "Your Name Here"
date: '`r format(Sys.time(), "%b %d, %Y")`'
output: bookdown::html_document2
---

```{r setup, include=FALSE}
library(dplyr)
library(MASS)
```


> Note: You are responsible for using the relevent libraries in the global options.

**Question 1**

For this problem we use the `birthwt` data frame from the `MASS` library. 

  a) Load the data and Use `?birthwt` in the console to look at the description of the data frame.
  
```{r}
# Answer here...

```
  



  b) We would like to predict the birth weight using the mother's age and mother's race.
  
  > Note: Notice that the `race` is coded using 1, 2 and 3. For conveniance I have added a new variable called `newRace` that has the races as `white`, `black` and `other`. Also, I created a new dataframe named `newBirthWt` which has the `newRace` variable in it.
  
  Copy and paste the following commands to create the new variable and the data frame. *Use this data frame throughout the rest of the problem.*
  
```{r}
newBirthWt <- birthwt %>%
  mutate(newRace = ifelse(race==1, "white", 
         ifelse(race==2, "black","other")))

head(newBirthWt)
```
   

  
  c) Conduct an EDA on the variables that we are interested in.
  
```{r}
# Answer here... Hint: EDA consists of 3 parts

```
  
  
  d) As a part of your EDA in part c) you should have created a scatterplot of `age` vs. `bwt` with colors and lines according to your `newRace` variable. Using this graph, decide whether to use a `parallel line model` or an `interaction model`. Explain.

```{r}
# Answer here... 

```


  e) Build the model you that you decided in part d). Name your model `wtModel`
  
```{r}
# Answer here... 

```
  



  f) Write the model (the whole model).
  
```{r}
# Answer here... 

```
  
  
        i. Write the model for the `black` mothers:

           Answer here... 

  
        
        ii. Write the model for the `white` mothers:
        
           Answer here... 

  
        
  
        iii. Write the model for the `other` mothers:
  
           Answer here... 


  g)  Create a new scatterplot of `age` vs. `bwt` with colors and lines according to your `newRace` variable using the model(s) you came up with in part f).
  
  
```{r}
# Answer here... 

```


  h) Create a residual plot and comment about the model.
  
```{r}
# Answer here... 

```
  

  i) Example: Assume that a white female is going to have a baby at the age of 25. Predict the baby's birth weight in grams. Remove the `#` in the following code. 
  
```{r}
#newdata = data.frame(age=25,  newRace = "white") # Define the new data point

#BabyWt <- predict(wtModel, newdata) # Use the predict function with the model

#cat("The baby will weigh about ", BabyWt, "grams") # Print the prediction
```
  
  
  Use the above example to predict the the baby's birth weight in grams for
  
        i) White female who is going to have a baby at the age of 36.
        
           Answer here... 

  
    
        ii) Black female who is going to have a baby at the age of 55.
        
           Answer here... 

  
    
        iii) A female from a different race than white or black who is going to have a baby at the age of 18.
        
           Answer here... 

  
    
  
  
  
  
  
  
  
  
  
  
  
  
  
  