---
title: "Lecture Notes for Ch 7 of MD: Multiple Regression"
author: "Dr. Hasthika Rupasinghe"
date: '`r format(Sys.time(), "%b %d, %Y at %X")`'
output:
  bookdown::html_document2:
    highlight: textmate
    theme: yeti
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center", comment = NA, options(scipen=999))
library(tidyverse)

library(knitr)

library(dplyr)
library(moderndive)

library(ggplot2)
library(dplyr)
library(moderndive)
library(ISLR)
library(skimr)
library(plotly)
```


```{r include=FALSE}
set.seed(417)

temp <- rnorm(100, mean=30, sd=5)
pressure <- rnorm(100)
dtime <- 1:100


plot_ly(x=temp, y=pressure, z=dtime, type="scatter3d", mode="markers", color=temp)
```

# Introduction

we’ll still use Credit to demonstrate multiple regression with:

  1. A numerical outcome variable y, in this case credit card balance.
  
  2. Two explanatory variables:
  
      + A first numerical explanatory variable $x_1$. In this case, their credit limit.
      
      + A second numerical explanatory variable  $x_2$. In this case, their income (in thousands of dollars).


# Exploratory data analysis

Let’s load the `Credit` data and: 

* Use the `View` command to look at raw data.
* Now `select()` only `Balance`, `Limit`, `Income`, `Rating` and `Age` variables. (We will use `Rating` and `Age` in a forthcoming exercise)


```{r echo=FALSE}
library(ISLR)
Credit <- Credit %>%
  select(Balance, Limit, Income, Rating, Age)
```
















