---
title: "R Markdown Basics"
author: "Dr. Hasthika Rupasinghe"
date: "1/16/2020"
output: html_document
---

#### Code Chunks

There is a in-built dataset in R called `cars`. Let's use it to get used to Rmarkdown.


```{r chunk_name}

head(cars)
summary(cars) # get all the information like mean, median from here

```

Note: Click on the `play` button to run the code chunk.

### Chunk Options

To hide your code chunk from the output use `echo=FALSE`.


```{r myHist, echo=FALSE}
hist(cars$speed)
```



Note: ERROR
Change the chunk_name

```{r no_code, echo=FALSE}


hist(cars$speed, xlab = "speed", main = "Histogram of Speed")



```

You use `results="hide"` to hide the results/output (but here the code would still be displayed).

```{r no_output, results="hide"}
cor(cars$speed,cars$dist)

```


You use `include=FALSE` to have the chunk evaluated, but neither the code nor its output displayed.

```{r no_output_no_code, include=FALSE}

cor(cars$speed,cars$dist)

```


### Figures

For figures, you’ll want to use options like fig.width and fig.height. For example:

```{r scatterplot, fig.width=6, fig.height=4, fig.align='center'}

plot(cars$speed,cars$dist)
?plot

```

Note: Change the height and width of the plot.

### In-line code

Here is an example of an in-line code.

There are `r nrow(cars)` cars in the `cars` dataset.
The highest speed recorded was `r max(cars)`.
The correlation between the `speed` and the `distane` is `r cor(cars$speed, cars$dist)`

Convert this html file to a pdf
Include the system date 
date: "`r Sys.Date()`"




