---
title: "Review for Exam 2"
author: "Dr. Hasthika Rupasinghe"
date: "04/07/2020"
output: html_document
---

This covers the review for Ch3. To review for Ch6 and Ch7, redo the examples in the lecture notes.


1) Use the `Recidivism` data from the `resampledata` library for this problem. Test the hypothesis that: The mean days to `Days` to reoffend for men is higher than for women?

  i) Assume that $\mu_{M}$ and $\mu_{W}$ be the mean `Days` to reoffend for men and women respectively. Write $H_0$ and $H_a$ for this problem.
  
$H_0: \mu_{M} = \mu_{W}$ vs. $H_a: \mu_{M} > \mu_{W}$

Important: Use `set.seed(10001)`

  ii) Conduct the test. Write your **complete** code here:
  
```{r include=FALSE}
library(resampledata)
library(dplyr)
```

Do this to get to know the variable names.

```{r}
data(Recidivism)
head(Recidivism)
```

Now start the test


```{r}
ANS <- Recidivism %>%
  group_by(Gender) %>%
  summarize(Average = mean(Days, na.rm = TRUE), count = n())
ANS

obs <- ANS[2, 2] - ANS[1, 2]
obs

observed <- obs$Average
observed


set.seed(10001)
sims <- 10^4 - 1 

ans <- numeric(sims)
for(i in 1:sims){
  index <- sample.int(n = 2101+14918, size = 14918, replace = FALSE)
  ans[i] <- mean(Recidivism$Days[index], na.rm = TRUE) - mean(Recidivism$Days[-index], na.rm = TRUE)
}

pvalue <- (sum(ans >= observed) + 1)/(sims + 1)
pvalue

```








  
```{r include=FALSE}

ANS <- Recidivism %>%
  group_by(Gender) %>%
  summarize(Average = mean(Days, na.rm = TRUE), N= n())
ANS


obs <- ANS[2,2] - ANS[1,2]
obs

obs_diff <- obs$Average
obs_diff # this is the observed diffrence


set.seed(10001)
sims <- 10^4 - 1 
ans <- numeric(sims)
for(i in 1:sims){
  index <- sample.int(n = 2101+14918, size = 14918, replace = FALSE)
  ans[i] <- mean(Recidivism$Days[index], na.rm = TRUE) - mean(Recidivism$Days[-index], na.rm = TRUE)
}

pvalue <- (sum(ans >= obs_diff) + 1)/(sims + 1)    # Notice >, this is because alternative hypothsis has >.
pvalue
```  
  
  
  
  
  
  
  
  
  
  
  iii) What is the $p$-value for this test?
  

 0.2479
 
     
  iv) Make the conclusion assuming $\alpha = 0.05$.
  
  a) Technical conclusion:
     
p-value = 0.2479 > 0.05, Fail to reject $H_0$ 

(Note: pvalue < alpha, Reject H0,  pvalue > alpha, Fail to Reject H0)
  
  b) Non-technical(English) conclusion:


There is NOT enough evidenace to conclude that the mean days to `Days` to reoffend for men is higher than for women








