---
title: "Lecture Notes for Ch3 of MD"
author: "Dr. Hasthika Rupasinghe"
date: '`r format(Sys.time(), "%b %d, %Y at %X")`'
output:
  bookdown::html_document2:
    highlight: textmate
    theme: yeti
---


# Data Visualization via ggplot2

We begin the development of your data science toolbox with data visualization. 

graphics provide a nice way for us to get a sense for how **quantitative** variables compare:

  1)  
  2) 

Examples of **quantitative** variables:

Also, plots/graphics help us to identify ___________ and ____________ in our data.

A common extension of these ideas is to compare the distribution of one quantitative variable  as we go across the levels of a different **categorical** variable.

Examples of **categorical** variables:

# Let's start by installing and loading the following pacakges

```{r}
library(nycflights13)
library(ggplot2)
library(dplyr)
```


We can break a graphic into the following essential(first three) components:

  * `data`: the data-set comprised of variables that we map.

  * `geom`: the geometric object in question. This refers to our type of objects we can observe in our plot. For example, points, lines, bars, etc.

  * `aes`: aesthetic attributes of the geometric object that we can perceive on a graphic. For example, x/y position, color, shape, and size. Each assigned aesthetic attribute can be mapped to a variable in our data-set.
  
  * `facet` ing breaks up a plot into small multiples corresponding to the levels of another variable (Section 3.6)
  
  * `position` adjustments for barplots (Section 3.8)

Let’s break down the grammar with an example.


We will be considering five different types of graphs. 

  1. scatterplots
  2. linegraphs
  3. boxplots
  4. histograms
  5. barplots
  
*Example:* We will graphically investigate the relationship between the following two numerical variables in the `flights` data frame:

  1. `dep_delay`: departure delay on the horizontal “x” axis and
  2. `arr_delay`: arrival delay on the vertical “y” axis

```{r}
#View(flights)
data(flights)
glimpse(flights)
```

Don’t worry for now if you don’t fully understand what this code is doing, we’ll explain this in details Chapter 5, just run it all and understand that we are taking all flights and only considering those corresponding to Alaska Airlines.

```{r}
all_alaska_flights <- flights %>% 
  filter(carrier == "AS")
```

```{r}
#View(all_alaska_flights)

```
  
## Scatter Plots:

```{r}
ggplot(data = all_alaska_flights, mapping = aes(x = dep_delay, y = arr_delay)) + 
  geom_point() 
```

The large mass of points near (0, 0) in this scatterplot can cause some confusion. We handdle this using

  1. By adjusting the ______________ of the points via the `________` argument:
  
```{r}
ggplot(data = all_alaska_flights, mapping = aes(x = dep_delay, y = arr_delay)) + 
  geom_point(alpha = 0.2) 
```
  
  2. By jittering the points via `geom_jitter()`:
  
  Here we are to adding just a bit of random noise to the points to better see them.
  
```{r}
ggplot(data = all_alaska_flights, mapping = aes(x = dep_delay, y = arr_delay)) + 
  geom_point() +
    geom_jitter(width = 30, height = 30)
```  
  
Question: 

  a. After viewing the Figure with `alpha` argument above, give an approximate range of arrival delays and departure delays that occur the most frequently. 
  
  
  b. How has that region changed compared to when you observed the same plot without the `alpha = 0.2`?


## Linegraphs

Explore the `weather` dataset from `nycflights13` package.

Type `library(nycflights13)` in the Console and hit return, then type `View(weather)` and hit return to view the data frame.

Let’s focus on the hourly temperature at Newark airport (origin code “EWR”) for the first 15 days in January 2013. 

```{r}

early_january_weather <- weather %>% 
  filter(origin == "EWR" & month == 1 & day <= 15)

```


```{r}
ggplot(data = early_january_weather, mapping = aes(x = time_hour, y = temp)) +
  geom_line()
```

Question: Plot a time series of a variable other than temp for Newark Airport in the first 15 days of January 2013.


```{r include=FALSE}

early_january_weather_1 <- weather %>% 
  filter(origin == "EWR" & month == 1 & day <= 15)

```

```{r include=FALSE}
ggplot(data = early_january_weather_1, mapping = aes(x = time_hour, y = humid)) +
  geom_line()
```








