---
title: "Quiz_2_v2"
author: "Lasanthi Watagoda"
date: "1/28/2019"
output: pdf_document
    
---

 Your Name ______________________

1. Suppose $n = 25$ and $X \sim N(1000, 81)$.What is the Distribution of $\bar{X}$

```{r}
# Answer:
#
#
#
#
#
```


2. Suppose $X\sim N(144,15)$ . Use `pnorm` to find $P(X \leq 100)$.
Write your `R` command & the answer.

```{r}
# Answer:
#
#
#
#
#
```

3. Open the `Auto` dataset in `ISLR` library. (Must use R commands)

  i) How many variables are in the Auto dataset & what is the sample size? 
```{r}
# Answer:
# 
#
#
#
#
```

  ii) What are the variables in Auto dataset? 
  
```{r}
# Answer:
# 
#
#
#
#
```

  
iii) What is the average `mpg`?

```{r}
# Answer:
# 
#
#
#
#
```

 iv) What is the highst `horsepower` recorded?
```{r}
# Answer:
# 
#
#
#
#
```

  v) Graph a histogram for `mpg` using `ggplot` (Hint: Load the ggplot2 library)
```{r}
# Answer: Sketch the graph here (label the axeses)
# 
#
#
#
#
#
#
#
#
#
#
```  
  
  vi) Graph a boxplot for `acceleration` using `ggplot`
```{r}
# Answer: Sketch the graph here (label the axeses)
# 
#
#
#
#
#
#
#
#
#
#
```  
  
  vii) Explain the boxplot in terms of Q1,Q2,Q3 and outliars.
```{r}
# Answer: 
# 
#
#
#
#
#
#
#
#
```

```{r include=FALSE}
library(ISLR)
library(ggplot2)
names(Auto)
str(Auto)
summary(Auto)
ggplot(data = Auto, aes(x= mpg)) + 
  geom_histogram() 

ggplot(data = Auto, aes(y= acceleration)) + 
  geom_boxplot() 
```

