---
title: "Quiz 02 - Version 02"
author: "Dr. Hasthika Rupasinghe"
date: '`r format(Sys.time(), "%b %d, %Y at %X")`'
output:
  bookdown::html_document2:
    highlight: textmate
    theme: yeti
---
  
1) Load the following `packages` in to `RStudio`

```{r message=FALSE}
library(nycflights13)
library(ggplot2)
library(dplyr)
```


2) The following code will load the `flights` dataframe and filter only the rows corresponding to American Airlines. Run this code.

```{r}
data(flights)

all_american_flights <- flights %>% 
  filter(carrier == "AA")
```


3) In this dataframe, the variable `air_time` is the amount of time spent in the air, in minutes. And, the variable `distance` is the distance between airports, in miles.

Create a scatterplot of the variables, `air_time` vs. the `distance` in the `all_american_flights` dataframe.

Hint: 

ggplot(data = _____________ , aes(x = ___________ , y = ___________)) + 
  geom_point() 

```{r}
# Your gode goes here

```


4) Adjust the transparency of the points via the `alpha` argument.


```{r}
# Your gode goes here

```


5) Describe the relationship between the variables `air_time` vs. the `distance`.

