---
title: "Quiz 03"
author: "Dr. Hasthika Rupasinghe"
date: "1/28/2019"
output: pdf_document
---

Name: __________________

1. Load the `Auto` dataset from the `ISLR` library. (Hint: Load the libary first, then load the data)

```{r}
# Answer:
# 
#
#
#
#
```


  i) How many variables (columns) are in the Auto dataset & what is the sample size (number of rows)? 
  
```{r}
# Answer:
# 
#
#
#
#
#
#
#
```

  ii) What are the names of variables in the `Auto` dataset? 
  
```{r}
# Answer:
# 
#
#
#
#
#
#
#
```

  
iii) What is the average `mpg`?

```{r}
# Answer:
# 
#
#
#
#
```

 iv) What is the highest `horsepower` recorded?
```{r}
# Answer:
# 
#
#
#
#
```

  v) Create a histogram for the variable `mpg`. **Use only 6 bins.** (Hint: Load the `ggplot2` library first)
```{r}
# Answer: Write the code here  and sketch the graph here (label the axeses)
# 
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
```  
  
  vi) Create a boxplot for to compare the `acceleration` among the levels of the `origin` variable.
  
```{r}
# Answer: Write the code here and sketch the graph (label the axeses)
# 
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
```  


```{r include=FALSE}
library(ISLR)
library(ggplot2)
names(Auto)
str(Auto)
summary(Auto)
ggplot(data = Auto, aes(x= mpg)) + 
  geom_histogram(bins = 6) 

ggplot(data = Auto, aes(y= acceleration, x = factor(origin))) + 
  geom_boxplot() 
```

