---
title: "Quiz 04"
author: "Dr. Hasthika Rupasinghe"
date: "02/07/2019"
output: pdf_document
---

Name: __________________

1. Load the `Recidivism` dataset from the `resampledata` library. (Hint: Load the libary first, then load the data)

```{r include=FALSE}
library(resampledata)
data(Recidivism)
```


```{r}
# Answer: Write the code here
# 
#
#
```


2) Use the `str` command to looke at the structure of the data and get to know the variable names. 

```{r include=FALSE}
str(Recidivism)
```


```{r}
# Answer: Only write the code, not the output
# 
#
#
```

&nbsp;

**For the rest of the problems, we only focus on two variables:**

    i. `Recid` - Whether they were sent back to prison or not
    ii. `Age25` - Whether they were under 25 years of age or not

&nbsp;

3) Create a barchart (using `ggplot`) and a table for the `Recid` variable

```{r include=FALSE}
library(ggplot2)
ggplot(data  = Recidivism, aes(x = Recid)) +
  geom_bar()

table(Recidivism$Recid)
```


```{r}
# Answer: Write the code, scatch the graph and the table
# 
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
```

  
4) Create a contingency table sumarizing the realtionship between recidivism (`Recid`) by age (`Age25`)

```{r include=FALSE}
table(Recidivism$Recid, Recidivism$Age25)
```

```{r}
# Answer: Write the code, scatch the table
# 
#
#
#
#
#
#
#
#
#
```

&nbsp;

5) Of those under 25 years of age, what proportion were sent back to prison? Of those under 25 years of age, what is that persentage?

Hint: Complete the follwoing code to answer the question.

    library(tidyverse)
    library(knitr)

    age25_back <- Recidivism %>%
      group_by(Age25) %>%
        summarize(Proportion = sum(________ == "___")/ sum(______ == "____" | _____ == "____"))

    kable(age25_back)

```{r include=FALSE}

library(tidyverse)
library(knitr)

age25_back <- Recidivism %>%
  group_by(Age25) %>%
  summarize(Proportion = sum(Recid == "Yes")/ sum(Recid == "Yes" | Recid == "No"))


kable(age25_back)


```

```{r}
# Answer: Complete the code above, scatch the table, answer the question.
# 
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
#
```



