---
title: "Quiz 05"
author: "Dr. Hasthika Rupasinghe"
date: "02/21/2019"
output: pdf_document
---

Name: __________________

1. Load the `Beerwings` dataset from the `resampledata` library. (Hint: Load the libary first, then load the data)

```{r include=FALSE}
library(resampledata)
data("Beerwings")
```


```{r}
# Answer: Write the code here
# 
#
#
```


2) `Beerwings`  data set description:

|Variable Name | Description| 
|:------|:----|
|`Gender`      | Male or Female|
|`Beer`      | Ounces of beer consumed| 
|`Hot Wings`      | Number of Hot Wings comsumned| 

Use the `str` command to looke at the structure of the data. 

```{r}
# Answer: Write the code here, do not write the output
# 
```


3) Do men consume more beer than females? Use a)-c) to in order to answer this question.

  a) Define your hypothesis ($H_0$ and $H_a$)
  
```{r}
# Answer: Answer
# 
#
```

  
  b) Conduct the test (Set your seed to `555`, do not forget to load the library `dplyr`)
  
```{r}
# Answer: Write your code here
# 
#
#
# 
#
#
# 
#
#
# 
#
#
# 
#
#
# 
#
# Write your p-value here (Hint: Answer should be close to 0.06)
# 
#
#
```

 c) Write the technical conclusion
 
```{r}
# Answer:
#
#
```

c) Write the non-technical conclusion
 
```{r}
# Answer:
#
#
#
```
 

```{r include=FALSE, comment=NA, message=FALSE}
library(dplyr)
library(knitr)

set.seed(555)
an <- Beerwings %>% 
  group_by(Gender) %>% 
  summarize(Mean = mean(Beer), N = n())
kable(an)

obs <- an[2,2] - an[1,2]
obs_diff <- obs$Mean
#
sims <- 10^4 - 1
md <- numeric(sims)
for(i in 1:sims){
  index <- sample(30, size = 15, replace = FALSE)
  md[i] <- mean(Beerwings$Beer[index]) - mean(Beerwings$Beer[-index])
}

pvalue <- 2*((sum(md >= obs_diff) + 1)/(sims + 1))
pvalue
```




